BOAST

### 2014-09-11 Tutorial/Tutorial-BOAST-2.tex
Updated tutorial

@@

\date{\textbf{BOAST Tutorial}\\June 25, 2014}

@@

\begin{frame}[fragile]
\frametitle{First interactive steps}
\lstset{language=Bash,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
Interactive Ruby:
\begin{lstlisting}
irb
\end{lstlisting}
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
Simple BOAST commands:
\begin{lstlisting}
irb(main):001:0> require 'BOAST'
=> true
irb(main):002:0> a = BOAST::Int "a"
=> a
irb(main):003:0> b = BOAST::Real "b"
=> b
irb(main):004:0> BOAST::decl a, b
integer(kind=4) :: a
real(kind=8) :: b
=> [a, b]
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Defining a Procedure}
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
Simple BOAST Procedure:
\footnotesize
\begin{lstlisting}
05:0> p = BOAST::Procedure( "test_proc", [a,b] )
06:0> BOAST::decl p
SUBROUTINE test_proc(a, b)
  integer, parameter :: wp=kind(1.0d0)
  integer(kind=4) :: a
  real(kind=8) :: b
007:0> BOAST::lang = BOAST::C
008:0> BOAST::decl p
void test_proc(int32_t a, double b){
009:0> BOAST::close p
}
\end{lstlisting}
Available languages are FORTRAN, C, CUDA, CL (OpenCL)
\end{frame}

\begin{frame}[fragile]
\frametitle{Defining a Full Procedure:}
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\tiny
\begin{lstlisting}
010:0> a = BOAST::Real( "a", :dir => :in)
011:0> b = BOAST::Real( "b", :dir => :out)
012:0> p = BOAST::Procedure( "test_proc", [a,b] ) { BOAST::print b === a + 2 }
013:0> BOAST::lang = BOAST::FORTRAN
014:0> BOAST::print p
SUBROUTINE test_proc(a, b)
    integer, parameter :: wp=kind(1.0d0)
    real(kind=8), intent(in) :: a
    real(kind=8), intent(out) :: b
    b = a + 2
END SUBROUTINE test_proc
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Creating a Computing Kernel}
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\tiny
\begin{lstlisting}
n = BOAST::Int(  "n", :dir => :in )
a = BOAST::Real( "a", :dir => :in,  :dim => [BOAST::Dim(n)] )
b = BOAST::Real( "b", :dir => :out, :dim => [BOAST::Dim(n)] )
p = BOAST::Procedure( "test_proc", [n, a, b] ) {
  BOAST::decl i = BOAST::Int( "i" )
  BOAST::For( i, 1, n ) {
    BOAST::print b[i] === a[i] + 2
  }.print
}
k = BOAST::CKernel::new
BOAST::print p
k.procedure = p
k.build
BOAST::verbose = true
k.build
> gcc -O2 -Wall -fPIC -I/usr/lib/ruby/1.9.1/x86_64-linux -I/usr/include/ruby-1.9.1 -I/usr/include/ruby-1.9.1/x86_64-linux -I/var/lib/gems/1.9.1/gems/narray-0.6.0.9 -DHAVE_NARRAY_H -c -o /tmp/Mod_test_proc20140624_19378_1qdep6u.o /tmp/Mod_test_proc20140624_19378_1qdep6u.c
> gfortran -O2 -Wall -fPIC -c -o /tmp/test_proc20140624-19378-1qdep6u.o /tmp/test_proc20140624-19378-1qdep6u.f90
> gcc -shared -o /tmp/Mod_test_proc20140624_19378_1qdep6u.so /tmp/Mod_test_proc20140624_19378_1qdep6u.o /tmp/test_proc20140624-19378-1qdep6u.o  -Wl,-Bsymbolic-functions -Wl,-z,relro -rdynamic -Wl,-export-dynamic  -L/usr/lib -lruby-1.9.1 -lrt
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Running a Computing Kernel}
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\tiny
\begin{lstlisting}
require 'narray'
input  = NArray.float(1024).random
output = NArray.float(1024)
n = BOAST::Int(  "n", :dir => :in )
a = BOAST::Real( "a", :dir => :in,  :dim => [BOAST::Dim(n)] )
b = BOAST::Real( "b", :dir => :out, :dim => [BOAST::Dim(n)] )
p = BOAST::Procedure( "test_proc", [n, a, b] ) {
  BOAST::decl i = BOAST::Int( "i" )
  BOAST::For( i, 1, n ) {
    BOAST::print b[i] === a[i] + 2
  }.print
}
k = BOAST::CKernel::new
BOAST::print p
k.procedure = p
k.run(input.length, input, output)
(output - input).each { |val| raise "Error!" if (val-2).abs > 1e-15 }
stats = k.run(input.length, input, output)
puts "#{stats[:duration]} s"
> 4.911e-06 s
\end{lstlisting}
\end{frame}

@@

\subsection{The Canonic Case}
\begin{frame}[fragile]
\frametitle{The Canonic Case: Vector Addition Kernel}
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
def BOAST::vector_add
  kernel = CKernel::new
  function_name = "vector_add"
  n = Int("n",{:dir => :in, :signed => false})
  a = Real("a",{:dir => :in, :dim => [ Dim(0,n-1)] })
  b = Real("b",{:dir => :in, :dim => [ Dim(0,n-1)] })
  c = Real("c",{:dir => :out, :dim => [ Dim(0,n-1)] })
  i = Int("i",{:signed => false})
  print p = Procedure(function_name, [n,a,b,c]) {
    decl i
    if [CL, CUDA].include?(get_lang) then
      print i === get_global_id(0)
      print c[i] === a[i] + b[i]
    else
      print For(i,0,n-1) {
        print c[i] === a[i] + b[i]
      }
    end
  }
  kernel.procedure = p
  return kernel
end
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Running the Kernel}
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
n = 1024*1024
a = NArray.float(n).random
b = NArray.float(n).random
c = NArray.float(n)
c_ref = NArray.float(n)

epsilon = 10e-15

set_lang( FORTRAN )
k = vector_add
k.run(n,a,b,c_ref)

[C, CL, CUDA].each { |lang|
  set_lang( lang )
  c.random
  k = vector_add
  case lang
  when CL
    k.run(n,a,b,c, :global_work_size => [rndup(n,32), 1,1], :local_work_size => [32,1,1] )
  when CUDA
    k.run(n,a,b,c, :block_number => [rndup(n,32)/32, 1,1], :block_size => [32,1,1] )
  else
    k.run(n,a,b,c)
  end
  (c_ref - c).abs.each { |diff|
    raise "Warning: residue too big: #{elem}" if elem > epsilon
  }
}
\end{lstlisting}
\end{frame}
\subsection{Building Kernels}
\begin{frame}[fragile]
\frametitle{Building Kernels}
\begin{itemize}
\item Running a kernel builds it (if it is not already built).
\item Kernels can be built beforehand.
\item Usual build parameters can be specified.
\end{itemize}
Sample:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  k.build({:FC => 'gfortran', :CC => 'gcc',\
           :FCFLAGS => "-O2", :LDFLAGS => ""})
  k.build({:FC => 'gfortran', :CC => 'gcc',\
           :FCFLAGS => "-O2 -fopenmp",:LDFLAGS => "-fopenmp"})
  k.build({:FC => 'ifort',    :CC => 'icc',
           :FCFLAGS => "-O2 -openmp" ,:LDFLAGS => "-openmp",:LD => "ifort"})
\end{lstlisting}
\normalsize
\begin{itemize}
\item Probes can be inserted at compile time.
\item Default: high resolution timer.
\end{itemize}
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  stats = k.run(...)
  puts stats[:duration]+" s"
\end{lstlisting}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{SPECFEM3D assemble\_boundary\_potential\_on\_device : BOAST (1)}
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
def BOAST::assemble_boundary_potential_on_device(ref = true)
  push_env( :array_start => 0 )
  kernel = CKernel::new
  function_name = "assemble_boundary_potential_on_device"
  num_interfaces                  = Int("num_interfaces",                   \
                                        :dir => :in)
  max_nibool_interfaces           = Int("max_nibool_interfaces",            \
                                        :dir => :in)
  d_potential_dot_dot_acoustic    = Real("d_potential_dot_dot_acoustic",    \
                                        :dir => :out,:dim => [ Dim() ])
  d_send_potential_dot_dot_buffer = Real("d_send_potential_dot_dot_buffer", \
                                        :dir => :in, :dim => [ Dim(num_interfaces*max_nibool_interfaces) ])
  d_nibool_interfaces             = Int("d_nibool_interfaces",              \
                                        :dir => :in, :dim => [ Dim(num_interfaces) ])
  d_ibool_interfaces              = Int("d_ibool_interfaces",               \
                                        :dir => :in, :dim => [ Dim(num_interfaces*max_nibool_interfaces) ])
  p = Procedure(function_name, [d_potential_dot_dot_acoustic,d_send_potential_dot_dot_buffer,num_interfaces,max_nibool_interfaces,d_nibool_interfaces,d_ibool_interfaces])
\end{lstlisting}

@@

\begin{frame}[fragile]
\frametitle{SPECFEM3D assemble\_boundary\_potential\_on\_device : BOAST (2)}
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  if(get_lang == CUDA and ref) then
    @@output.print File::read("specfem3D/#{function_name}.cu")
  elsif(get_lang == CUDA or get_lang == CL) then
    decl p
    id         = Int("id")
    iglob      = Int("iglob")
    iloc       = Int("iloc")
    iinterface = Int("iinterface")
    decl id, iglob, iloc, iinterface
    print id === get_global_id(0) + get_global_size(0)*get_global_id(1)
    print For(iinterface, 0, num_interfaces-1) {
      print If(id<d_nibool_interfaces[iinterface]) {
        print iloc === id + max_nibool_interfaces*iinterface
        print iglob === d_ibool_interfaces[iloc] - 1
        print atomicAdd(d_potential_dot_dot_acoustic + iglob, \
                        d_send_potential_dot_dot_buffer[iloc])
      }
    }
    close p
  else
    raise "Unsupported language!"
  end
  pop_env( :array_start )
  kernel.procedure = p
  return kernel
end
\end{lstlisting}

@@

__kernel void assemble_boundary_potential_on_device(__global float * d_potential_dot_dot_acoustic, const __global float * d_send_potential_dot_dot_buffer, const int num_interfaces, const int max_nibool_interfaces, const __global int * d_nibool_interfaces, const __global int * d_ibool_interfaces){
  int id;
  int iglob;
  int iloc;
  int iinterface;
  id = get_global_id(0) + ((get_global_size(0)) * (get_global_id(1)));
  for(iinterface=0; iinterface<=num_interfaces - (1); iinterface+=1){
    if(id < d_nibool_interfaces[iinterface - 0]){
      iloc = id + ((max_nibool_interfaces) * (iinterface));
      iglob = d_ibool_interfaces[iloc - 0] - (1);
      atomicAdd(d_potential_dot_dot_acoustic + (iglob), d_send_potential_dot_dot_buffer[iloc - 0]);
    }
  }
}
\end{lstlisting}
\end{frame}
\begin{frame}
\frametitle{BigDFT Synthesis Kernel}
\centering 
\includegraphics[scale=0.5]{Res_synthesis}\\

>>>>

\lstdefinestyle{BOAST}{
  language=Ruby,
  basicstyle=\tiny\ttfamily,
  backgroundcolor=\color{white},
  frame=single,
  captionpos=b,
  morekeywords={BOAST, pr, decl, open, close}
}

@@

\date{\textbf{BOAST Tutorial}\\September 19, 2014}

@@

\begin{frame}[fragile]
\frametitle{First interactive steps}
\lstset{language=Bash,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
Interactive Ruby:
\begin{lstlisting}
irb
\end{lstlisting}
Simple BOAST commands:
\lstset{style=BOAST}
\begin{lstlisting}
irb(main):001:0> require 'BOAST'
=> true
irb(main):002:0> a = BOAST::Int "a"
=> a
irb(main):003:0> b = BOAST::Real "b"
=> b
irb(main):004:0> BOAST::decl a, b
integer(kind=4) :: a
real(kind=8) :: b
=> [a, b]
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Defining a Procedure}
Simple BOAST Procedure:
\lstset{style=BOAST}
\footnotesize
\begin{lstlisting}
05:0> p = BOAST::Procedure( "test_proc", [a,b] )
06:0> BOAST::open p
SUBROUTINE test_proc(a, b)
  integer, parameter :: wp=kind(1.0d0)
  integer(kind=4) :: a
  real(kind=8) :: b
007:0> BOAST::lang = BOAST::C
008:0> BOAST::decl p
void test_proc(int32_t a, double b){
009:0> BOAST::close p
}
\end{lstlisting}
Available languages are FORTRAN, C, CUDA, CL (OpenCL)
\end{frame}

\begin{frame}[fragile]
\frametitle{Defining a Full Procedure:}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
010:0> a = BOAST::Real( "a", :dir => :in)
011:0> b = BOAST::Real( "b", :dir => :out)
012:0> p = BOAST::Procedure( "test_proc", [a,b] ) {
012:1>   BOAST::pr b === a + 2
012:2> }
013:0> BOAST::lang = BOAST::FORTRAN
014:0> BOAST::pr p
SUBROUTINE test_proc(a, b)
    integer, parameter :: wp=kind(1.0d0)
    real(kind=8), intent(in) :: a
    real(kind=8), intent(out) :: b
    b = a + 2
END SUBROUTINE test_proc
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Creating a Computing Kernel}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
n = BOAST::Int(  "n", :dir => :in )
a = BOAST::Real( "a", :dir => :in,  :dim => [BOAST::Dim(n)] )
b = BOAST::Real( "b", :dir => :out, :dim => [BOAST::Dim(n)] )
p = BOAST::Procedure( "test_proc", [n, a, b] ) {
  BOAST::decl i = BOAST::Int( "i" )
  BOAST::pr BOAST::For( i, 1, n ) {
    BOAST::pr b[i] === a[i] + 2
  }
}
k = BOAST::CKernel::new
BOAST::pr p
k.procedure = p
k.build
BOAST::verbose = true
k.build
> gcc -O2 -Wall -fPIC -I/usr/lib/ruby/1.9.1/x86_64-linux -I/usr/include/ruby-1.9.1 -I/usr/include/ruby-1.9.1/x86_64-linux -I/var/lib/gems/1.9.1/gems/narray-0.6.0.9 -DHAVE_NARRAY_H -c -o /tmp/Mod_test_proc20140624_19378_1qdep6u.o /tmp/Mod_test_proc20140624_19378_1qdep6u.c
> gfortran -O2 -Wall -fPIC -c -o /tmp/test_proc20140624-19378-1qdep6u.o /tmp/test_proc20140624-19378-1qdep6u.f90
> gcc -shared -o /tmp/Mod_test_proc20140624_19378_1qdep6u.so /tmp/Mod_test_proc20140624_19378_1qdep6u.o /tmp/test_proc20140624-19378-1qdep6u.o -Wl,-Bsymbolic-functions -Wl,-z,relro -rdynamic -Wl,-export-dynamic -L/usr/lib -lruby-1.9.1 -lrt
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Running a Computing Kernel}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
require 'narray'
input  = NArray.float(1024).random
output = NArray.float(1024)
n = BOAST::Int(  "n", :dir => :in )
a = BOAST::Real( "a", :dir => :in,  :dim => [BOAST::Dim(n)] )
b = BOAST::Real( "b", :dir => :out, :dim => [BOAST::Dim(n)] )
p = BOAST::Procedure( "test_proc", [n, a, b] ) {
  BOAST::decl i = BOAST::Int( "i" )
  BOAST::pr BOAST::For( i, 1, n ) {
    BOAST::pr b[i] === a[i] + 2
  }
}
k = BOAST::CKernel::new
BOAST::pr p
k.procedure = p
k.run(input.length, input, output)
(output - input).each {
  |val| raise "Error!" if (val-2).abs > 1e-15 }
stats = k.run(input.length, input, output)
puts "#{stats[:duration]} s"
> 4.911e-06 s
\end{lstlisting}
\end{frame}

@@

\subsection{The Canonic Case}
\begin{frame}[fragile]
\frametitle{The Canonic Case: Vector Addition Kernel}
\tiny
\lstset{style=BOAST}
\begin{lstlisting}
def BOAST::vector_add
  kernel = CKernel::new
  function_name = "vector_add"
  n = Int("n",{:dir => :in, :signed => false})
  a = Real("a",{:dir => :in, :dim => [ Dim(0,n-1)] })
  b = Real("b",{:dir => :in, :dim => [ Dim(0,n-1)] })
  c = Real("c",{:dir => :out, :dim => [ Dim(0,n-1)] })
  i = Int("i",{:signed => false})
  pr p = Procedure(function_name, [n,a,b,c]) {
    decl i
    if [CL, CUDA].include?(get_lang) then
      pr i === get_global_id(0)
      pr c[i] === a[i] + b[i]
    else
      pr For(i,0,n-1) {
        pr c[i] === a[i] + b[i]
      }
    end
  }
  kernel.procedure = p
  return kernel
end
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Running the Kernel}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
n = 1024*1024
a = NArray.float(n).random
b = NArray.float(n).random
c = NArray.float(n)
c_ref = NArray.float(n)
epsilon = 10e-15
set_lang( FORTRAN )
k = vector_add
k.run(n,a,b,c_ref)
[C, CL, CUDA].each { |lang|
  set_lang( lang )
  c.random
  k = vector_add
  case lang
  when CL
    k.run(n,a,b,c, :global_work_size => [rndup(n,32), 1,1], :local_work_size => [32,1,1] )
  when CUDA
    k.run(n,a,b,c, :block_number => [rndup(n,32)/32, 1,1], :block_size => [32,1,1] )
  else
    k.run(n,a,b,c)
  end
  (c_ref - c).abs.each { |diff|
    raise "Warning: residue too big: #{elem}" if elem > epsilon
  }
}
\end{lstlisting}
\end{frame}
\subsection{Building Kernels}
\begin{frame}[fragile]
\frametitle{Building Kernels}
\begin{itemize}
\item Running a kernel builds it (if it is not already built).
\item Kernels can be built beforehand.
\item Usual build parameters can be specified.
\end{itemize}
Sample:
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
  k.build({:FC => 'gfortran', :CC => 'gcc',\
           :FCFLAGS => "-O2", :LDFLAGS => ""})
  k.build({:FC => 'gfortran', :CC => 'gcc',\
           :FCFLAGS => "-O2 -fopenmp",:LDFLAGS => "-fopenmp"})
  k.build({:FC => 'ifort',    :CC => 'icc',
           :FCFLAGS => "-O2 -openmp" ,:LDFLAGS => "-openmp",:LD => "ifort"})
\end{lstlisting}
\normalsize
\begin{itemize}
\item Probes can be inserted at compile time.
\item Default: high resolution timer.
\end{itemize}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
  stats = k.run(...)
  puts stats[:duration]+" s"
\end{lstlisting}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{SPECFEM3D assemble\_boundary\_potential\_on\_device : BOAST (1)}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
def BOAST::assemble_boundary_potential_on_device(ref = true)
  push_env( :array_start => 0 )
  kernel = CKernel::new
  function_name = "assemble_boundary_potential_on_device"
  num_interfaces                  = Int("num_interfaces",                   \
                                        :dir => :in)
  max_nibool_interfaces           = Int("max_nibool_interfaces",            \
                                        :dir => :in)
  d_potential_dot_dot_acoustic    = Real("d_potential_dot_dot_acoustic",    \
                                        :dir => :out,:dim => [ Dim() ])
  d_send_potential_dot_dot_buffer = Real("d_send_potential_dot_dot_buffer", \
                                        :dir => :in, :dim => [ Dim(num_interfaces*max_nibool_interfaces) ])
  d_nibool_interfaces             = Int("d_nibool_interfaces",              \
                                        :dir => :in, :dim => [ Dim(num_interfaces) ])
  d_ibool_interfaces              = Int("d_ibool_interfaces",               \
                                        :dir => :in, :dim => [ Dim(num_interfaces*max_nibool_interfaces) ])
  p = Procedure(function_name, [d_potential_dot_dot_acoustic,d_send_potential_dot_dot_buffer,num_interfaces,max_nibool_interfaces,d_nibool_interfaces,d_ibool_interfaces])
\end{lstlisting}

@@

\begin{frame}[fragile]
\frametitle{SPECFEM3D assemble\_boundary\_potential\_on\_device : BOAST (2)}
\lstset{style=BOAST}
\tiny
\begin{lstlisting}
  if(get_lang == CUDA and ref) then
    @@output.print File::read("specfem3D/#{function_name}.cu")
  elsif(get_lang == CUDA or get_lang == CL) then
    open p
    id         = Int("id")
    iglob      = Int("iglob")
    iloc       = Int("iloc")
    iinterface = Int("iinterface")
    decl id, iglob, iloc, iinterface
    pr id === get_global_id(0) + get_global_size(0)*get_global_id(1)
    pr For(iinterface, 0, num_interfaces-1) {
      pr If(id<d_nibool_interfaces[iinterface]) {
        pr iloc === id + max_nibool_interfaces*iinterface
        pr iglob === d_ibool_interfaces[iloc] - 1
        pr atomicAdd(d_potential_dot_dot_acoustic + iglob, \
                     d_send_potential_dot_dot_buffer[iloc])
      }
    }
    close p
  else
    raise "Unsupported language!"
  end
  pop_env( :array_start )
  kernel.procedure = p
  return kernel
end
\end{lstlisting}

@@

__kernel void assemble_boundary_potential_on_device(__global float * d_potential_dot_dot_acoustic, const __global float * d_send_potential_dot_dot_buffer, const int num_interfaces, const int max_nibool_interfaces, const __global int * d_nibool_interfaces, const __global int * d_ibool_interfaces){
  int id;
  int iglob;
  int iloc;
  int iinterface;
  id = get_global_id(0) + ((get_global_size(0)) * (get_global_id(1)));
  for(iinterface=0; iinterface<=num_interfaces - (1); iinterface+=1){
    if(id < d_nibool_interfaces[iinterface - 0]){
      iloc = id + ((max_nibool_interfaces) * (iinterface));
      iglob = d_ibool_interfaces[iloc - 0] - (1);
      atomicAdd(d_potential_dot_dot_acoustic + (iglob), d_send_potential_dot_dot_buffer[iloc - 0]);
    }
  }
}
\end{lstlisting}
\end{frame}
%\begin{frame}
%\frametitle{BigDFT Synthesis Kernel}
%\centering 
%\includegraphics[scale=0.5]{Res_synthesis}\\
%
%
%\end{frame}

### 2014-09-11 Tutorial/Tutorial-BOAST.tex
Updated tutorial

\date{\textbf{Tutorial BOAST}\\June 25, 2014}

@@

\begin{frame}[fragile]
\frametitle{Sample Code: Procedure Declaration}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
p = Procedure("magic_filter", [n,ndat,x,y], [lowfil,upfil])
decl p
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
subroutine magicfilter(n, ndat, x, y)
  integer(kind=4), parameter :: lowfil = -8
  integer(kind=4), parameter :: upfil = 7
  integer(kind=4), intent(in) :: n
  integer(kind=4), intent(in) :: ndat
  real(kind=8), intent(in), dimension(0:n-1, ndat) :: x
  real(kind=8), intent(out), dimension(ndat, 0:n-1) :: y
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
void magicfilter(const int32_t n, const int32_t ndat, const double * x, double * y){
  const int32_t lowfil = -8;
  const int32_t upfil = 7;
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Sample Code: Constructs and Arrays}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  unroll = 5
  print For(j,1,ndat-(unroll-1), unroll) {
  #.....
    (tt2 === tt2 + x[k,j+1]*fil[l]).print
  #.....
  }
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  do j=1, ndat-4, 5
    !......
    tt2=tt2+x(k,j+1)*fil(l)
    !......
  enddo
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  for(j=1; j<=ndat-4; j+=5){
  /*...........*/
    tt2=tt2+x[k-0+(j+1-1)*(n-1-0+1)]*fil[l-lowfil];
  /*...........*/
  }
\end{lstlisting}
\end{frame}

>>>>

\date{\textbf{Tutorial BOAST}\\September 19, 2014}

@@

\begin{frame}[fragile]
\frametitle{Sample Code: Procedure Declaration}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
p = Procedure("magic_filter", [n,ndat,x,y], [lowfil,upfil])
open p
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
subroutine magicfilter(n, ndat, x, y)
  integer(kind=4), parameter :: lowfil = -8
  integer(kind=4), parameter :: upfil = 7
  integer(kind=4), intent(in) :: n
  integer(kind=4), intent(in) :: ndat
  real(kind=8), intent(in), dimension(0:n-1, ndat) :: x
  real(kind=8), intent(out), dimension(ndat, 0:n-1) :: y
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
void magicfilter(const int32_t n, const int32_t ndat, const double * x, double * y){
  const int32_t lowfil = -8;
  const int32_t upfil = 7;
\end{lstlisting}
\end{frame}

\begin{frame}[fragile]
\frametitle{Sample Code: Constructs and Arrays}
The following declaration:
\tiny
\lstset{language=Ruby,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  unroll = 5
  pr For(j,1,ndat-(unroll-1), unroll) {
  #.....
    pr tt2 === tt2 + x[k,j+1]*fil[l]
  #.....
  }
\end{lstlisting}
\normalsize 
Outputs Fortran:
\tiny
\lstset{language=Fortran,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  do j=1, ndat-4, 5
    !......
    tt2=tt2+x(k,j+1)*fil(l)
    !......
  enddo
\end{lstlisting}
\normalsize
Or C:
\tiny
\lstset{language=C,
basicstyle=\ttfamily,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
numbers=left,
tabsize=4,
showspaces=false,
showstringspaces=false}
\begin{lstlisting}
  for(j=1; j<=ndat-4; j+=5){
  /*...........*/
    tt2=tt2+x[k-0+(j+1-1)*(n-1-0+1)]*fil[l-lowfil];
  /*...........*/
  }
\end{lstlisting}
\end{frame}
